\textbf{\sc Towards Deliberative Control in Marine Robotics}

### 2012-02-24 trunk/future.tex
Added few paragraphs in future work more related to T-REX refinements

\begin{figure}[h]
  \centering
  \includegraphics[scale=0.45]{figs/autonomy-topics.pdf}
  \caption{\small }
  \label{fig:topics}
\end{figure}

@@

>>>>

\begin{figure}[h]
  \centering
  \includegraphics[scale=0.45]{figs/autonomy-topics.pdf}
  \caption{\small Overlapping topics in our research in deliberation
    and autonomy with sampling the dominant theme.}
  \label{fig:topics}
\end{figure}

@@

Many aspect remain to be fully explored in how to improve \rx and its
integration with \eu. We present here  few of these that we consider
as important in order to improve \rx abilities and reduce the
engineering required to circonvey them.

One of them is related to the dispatchability of
the {\em external} part of the plan \cite{mus98a}. While we were able
to limit its impact so far by adding extra controls inside the \eu
model we know that it can be impoved. For example by analyzing the
plan structure we dshould be able to distinguish part of the plan that
contribute to a  reactor goal -- which often needs to be dispatched
as early as possible -- to other tokens describing the world evolution
for which it can be preferrable to dispatch as late as needed. Being
able to distinguish these two kinds of tokens should largely improve
the quality of the overal agent behavior while avoiding to add extra
complexity on every reactor models.

At the architecture level we would like to take full benefits of the
reactor graph structure maintained by the agent and how to take full
benefits. One aspect, we need to improve further is the ability to
alter this graph dynamically by creating new reactors or new timeline
connections. Offering such abilty would allow to provide better
reovery mechanism after one reactor has failed to sunchronize by the 
agent. For example, one alternate reactor could take ownership of the
timelines left invalid by the destruction of the faulty reactor. This
would allow to dimplement in atrasnparent way components
redudancy. Still, even though our implementation already allow such
mechanism we do not provide yet this at \rx API level as we need to
ensure that this kind of dynamic alteration of the graph can be done
wothout breaking our current assumptions both at \rx level and \eu
level.

More specifically to \eu level we would like to improve \rx
integration of \eu ability to deliberate about resources. More
specifically we need to ba able to update resource level as 
modeled by \eu based on \rx observation.  As of today the 
support of resource is limited inside the \eu solver and there's no
direct way for \rx to update them dynamically based on recent
observations. This result on a potential discrepeancy between measured
given by, for example, the battery as modeled in \eu and the current
battery level as read in a \rx timeline. Finding an automated way to
link these two constructs would allow the plan to dynamically readapt
when these two values differs -- for example if the vehicle looses a
battery bank during a mission.

### 2012-02-24 trunk/results.tex
Added few paragraphs in future work more related to T-REX refinements

The novelty in this application was two-fold; in enabling the
deliberation to decide when to decide on the phase changes and in
showing viably how a human being coupled with a goal-oriented
controller could do problem solving jointly. The approach, is general
and can be adapted to any feature or scalar field.

@@

To augment our understanding of such microbial communities, the Dorado
with \rx has been utilized in a range of activities in a
quasi-lagrangian mode. As the water mass is being tracked with a
drifting instrument, the vehicle is expected to move around it. While
a number of different patterns have been tested in simulation, the
majority of at-sea deployments have used a square pattern ($3X3$
km\textsuperscript{2} or a $1X1$ km\textsuperscript{2})\footnote{Often
  post-hoc reconstruction of the data set for visualization drives how
  much adaptation the vehicle can be allowed to undertake.}. Plan
synthesis occurs frequently, but within the context of a drifting
point generated by a drifter. Fig. \ref{fig:dta-setup} shows the
general setup of our experiments which can be tailored with the use of
various computational methods within the \texttt{DTA} app which is
contained within the Oceanographic Decision Support System (\od; see
below) \cite{das11}. GPS data from the free-floating drifter is sent
via satellite and processed onshore to determine a projection (speed
and bearing) of the drifter. This data is sent to the AUV; at the
completion of the current survey, the vehicle receives this data as a
high-level goal which is decomposed and synthesized as a survey
plan. Currently, the vehicle completes the survey without any further
dynamic updates from the drifter. In order to minimize the range of
errors that the survey needs to encapsulate (data latency or surface
or sub-surface currents for those drifters which have a drogue) the
estimation is a projection in time and space of the drifters centroid
sent with this goal from the shore-side app.

>>>>

The novelty in this application was two-fold; in enabling the
deliberation to decide when to trigger the phase changes and in
showing viably how a human being coupled with a goal-oriented
controller could do problem solving jointly. The approach, is general
and can be adapted to any feature or scalar field.

@@

To augment our understanding of such microbial communities, the Dorado
with \rx has been utilized in a range of activities in a
quasi-lagrangian mode. As the water mass is being tracked with a
drifting instrument, the vehicle is expected to move around it. While
our model suppirt multiples patterns(square, lawn-mower,
transect(s)\dots) with any possible dimension factor, the
majority of at-sea deployments have used a square pattern ($3X3$
km\textsuperscript{2} or a $1X1$ km\textsuperscript{2})\footnote{Often
  post-hoc reconstruction of the data set for visualization drives how
  much adaptation the vehicle can be allowed to undertake.}. Plan
synthesis occurs frequently, but within the context of a drifting
point generated by a drifter. Fig. \ref{fig:dta-setup} shows the
general setup of our experiments which can be tailored with the use of
various computational methods within the \texttt{DTA} app which is
contained within the Oceanographic Decision Support System (\od; see
below) \cite{das11}. GPS data from the free-floating drifter is sent
via satellite and processed onshore to determine a projection (speed
and bearing) of the drifter. This data is sent to the AUV; at the
completion of the current survey, the vehicle receives this data as a
high-level goal which is decomposed and synthesized as a survey
plan. Currently, the vehicle completes the survey without any further
dynamic updates from the drifter. In order to minimize the range of
errors that the survey needs to encapsulate (data latency or surface
or sub-surface currents for those drifters which have a drogue) the
estimation is a projection in time and space of the drifters centroid
sent with this goal from the shore-side app.
